\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-07-30 introduction.tex
preparing for submission to soft robotics journal

\subsection{Related Work}
There are several examples of soft grippers described in recent literature, \rkk{we will mainly focus on fluidic-based systems.} 
Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human\cite{deimel2014novel}. 
Ilievski et al. \cite{ilievski2011soft} create \rkk{through a soft-lithography fabrication} a pneumatic starfish-like gripper composed of \rkk{an array of silicone chambers and a PDMS membrane.} 
\rkk{
The gripper is hanging on a string and grasps objects like an egg or a mouse in an open-loop controlled manner.
} 
Stokes et al. \cite{Stokes2014hybrid} use a soft elastomer quadrupedal robot to grasp objects in a hard-soft hybrid robotic platform. 
A puncture resistant soft pneumatic gripper is developed by Shepherd et al. in \cite{shepherd2013soft}. 
An alternative to positive pressure actuated soft grippers is a robotic gripper that makes use of granular material jamming developed by Brown et al. and detailed in \cite{brown2010universal}.
\rkk{The soft octopus-inspired arms developed in \cite{calisti2010study} and \cite{calisti2011octopus} are not fluidic powered, but instead use cables to pull rigid fixtures embedded within an elastomer body. 
The arms were capable of grasping objects like pens or screws.}
A soft robotic tentacle developed in \cite{martinez2013robotic} was able to hold a flower and a horseshoe-shaped object.
The closest related soft pneumatic actuator design to our current work is the fast Pneu-net designs by Mosadegh et al. detailed in \cite{mosadegh2014pneumatic} and by Polygerinos et al. detailed in \cite{polygerinos2013towards}.
These finger-like actuators deform with minimal volume change and can bend to high curvatures.
\rkk{None of the above described grippers were controlled autonomously to perform their tasks and accordingly no statement on repeatability of the autonomous execution was given.}

>>>>

\subsection{Related Work}
There are several examples of soft grippers described in recent literature, \rkk{we will mainly focus on fluidic-based systems.} 
Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human \cite{deimel2014novel}. 
Ilievski et al. \cite{ilievski2011soft} create \rkk{through a soft-lithography fabrication} a pneumatic starfish-like gripper composed of \rkk{an array of silicone chambers and a PDMS membrane.} 
\rkk{
The gripper is hanging on a string and grasps objects like an egg or a mouse in an open-loop controlled manner.
} 
Stokes et al. \cite{Stokes2014hybrid} use a soft elastomer quadrupedal robot to grasp objects in a hard-soft hybrid robotic platform. 
A puncture resistant soft pneumatic gripper is developed by Shepherd et al. in \cite{shepherd2013soft}. 
An alternative to positive pressure actuated soft grippers is a robotic gripper that makes use of granular material jamming developed by Brown et al. and detailed in \cite{brown2010universal}.
\rkk{The soft octopus-inspired arms developed in \cite{calisti2010study} and \cite{calisti2011octopus} are not fluidic powered, but instead use cables to pull rigid fixtures embedded within an elastomer body. 
The arms were capable of grasping objects like pens or screws.}
A soft robotic tentacle developed in \cite{martinez2013robotic} was able to hold a flower and a horseshoe-shaped object.
The closest related soft pneumatic actuator design to our current work is the fast Pneu-net designs by Mosadegh et al. \cite{mosadegh2014pneumatic} and by Polygerinos et al. \cite{polygerinos2013towards}.
These finger-like actuators deform with minimal volume change and can bend to high curvatures.
\rkk{None of the above described grippers were controlled autonomously to perform their tasks and accordingly no statement on repeatability of the autonomous execution was given.}

### 2015-07-30 katzschmann2015autonomous.tex
preparing for submission to soft robotics journal

\usepackage{multirow}
\usepackage{setspace} % This is used in the title page
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{amsmath, amssymb, graphics, setspace}
\usepackage{caption}
%\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[noend]{algpseudocode}
\usepackage{longtable}
\usepackage{natbib}
\bibliographystyle{plainnat}
%\usepackage{section}{placeins}
\usepackage{float}
\usepackage{hyperref}
\usepackage[section]{placeins}

@@

\section*{ACKNOWLEDGMENTS}
This research was conducted in the Distributed Robotics Laboratory at MIT with support from the National Science Foundation, grant numbers NSF 1117178, NSF EAGER 1133224, NSF IIS1226883 and NSF CCF1138967, and National Science Foundation Graduate Research Fellowship Program, primary award number 1122374. We are grateful for this support.

>>>>

\usepackage{multirow}
\usepackage{setspace} % This is used in the title page
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{amsmath, amssymb, graphics, setspace}
\usepackage{caption}
%\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[noend]{algpseudocode}
\usepackage{longtable}
\usepackage{natbib}
\bibliographystyle{plain}
%\usepackage{section}{placeins}
\usepackage{float}
\usepackage{hyperref}
\usepackage[section]{placeins}

@@

\section*{ACKNOWLEDGMENTS}
This research was conducted in the Distributed Robotics Laboratory at MIT with support from the National Science Foundation, grant numbers NSF 1117178, NSF IIS1226883 and NSF CCF1138967, and National Science Foundation Graduate Research Fellowship Program, primary award number 1122374. We are grateful for this support.
